\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{setspace}

\setlength\parindent{0pt}
\usepackage{hyperref}
\usepackage{amssymb,amsthm,amsmath, fancyhdr}
\pagestyle{fancy}

\usepackage{lipsum}

\begin{document}
\chead{Math 121 - Continuity and the Intermediate Value Theorem}
\begin{enumerate}
\item What is the definition of continuity? 
\item What types of functions are stated to be continuous in Theorem 6 in Section 1.5?
\item It is given in the text that all trigonometric functions are continuous at all points in their domain. Show why this function is continuous at all points in $(-\infty, \infty)$. There's really only one thing you need to check. What is it?
$$f(x) = \left\{ \begin{array}{rl} \sin(x) & \mbox{if } x < \pi/4\\ \cos(x) & \mbox{if } x \geq \pi/4 \end{array}\right.$$
\item Write a function that isn't continuous at $x = 2$ or at $x = -2$.
\item We can apply the Intermediate Value Theorem to show that an equation has a solution in a given interval.

Consider the equation $2x^3 + 7x - 5 = 0$. I claim that this has a solution in the interval (0,2). Let's use IVT to show that this works.

\begin{itemize}
\item Is the function $f(x) = 2x^3 + 7x -5$ continuous on the interval (0,2)?
\item What is the value of $f(0)$?
\item What is the value of $f(2)$?
\item What must have happened to the graph of the function $f(x)$ between $f(0)$ and $f(2)$, and why does this mean our original equation has a solution?
\end{itemize}
\item Suppose a monk rises in the morning, and starts to walk up a mountain. He starts at 7 am, and reaches the peak at 7 pm. He spends the night, and starts down the mountain at 7 am, arriving back at his home at 7 pm. Show that there is at least one point on the mountain that the monk will walk past at the same time on both days.

Try graphing his elevation as a function of time. You can do this with two graphs, one going up, and the other going down, on the same sheet of paper. What has to happen?
\end{enumerate}
\end{document}