\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{fancyhdr}
\usepackage[margin=1.0in]{geometry}
\usepackage{amsmath}
\usepackage{changepage,stackrel}
\usepackage{graphicx}
\usepackage[inline]{enumitem}
\usepackage{enumitem}
\pagestyle{fancy}
\chead{Math 121 - Integrating with Substitution}

\begin{document}
For each of these definite integrals, evaluate by returning to the original variable after the substitution.
\begin{enumerate}
    \item $\int_{-2}^0 2x^2\sqrt{1 - 4x^3} dx$
    \item $\int_{-1}^5 (1+w)(2w + w^2)^5 dw$
    \item $\int_{\pi/3}^0 3\sin(x/2)dx$
    \item $\int_{-\pi}^{\pi/2} \cos(t)\cos(\sin(t))dt$
\end{enumerate}
For each definite integral above, when you make the substitution, use your function for $u$ to change the bounds of integration. Then evaluate the integral before you return to the original variable. Your results should match what you found above.

\begin{enumerate}
    \setcounter{enumi}{4}
    \item Find the area between the curves $y = 2x^2 + 10$ and $y = 4x + 16$ over the interval [-2,5].
    \item Find the area bounded by the curves $y = x^2$ and $y = \sqrt{x}$.
    \item A spring has a natural length of 20 $cm$. A 40 $N$ force is required to stretch (and hold the spring) to a length of 30 $cm$. How much work is done in stretching the spring from $35$ $cm$ to 38 $cm$?
    \begin{itemize}
        \item The law we need here is Hooke's Law, $F(x) = kx$. This is the force required to stretch a spring $x$ meters from it's natural length.
        \item You have the force needed to stretch the spring 10 $cm$, or $0.1m$ from the problem. Use this to find $k$.
        \item If the natural length is 20 $cm$, we can treat that like 0 when determining the bounds of an integral. So a spring stretched to 35 $cm$ is really stretched $0.15m$ away from 0. What value should you use for 38 $cm$?
        \item Integrate $F(x)$, using the value of $k$ you found above, over the inteval in meters, from 35 $cm$ to 38 $cm$. The value you find is the amount of work, in Joules, needed to stretch the spring.
    \end{itemize}
\end{enumerate}
\end{document}