\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{fancyhdr}
\usepackage[margin=1.0in]{geometry}
\usepackage{amsmath}
\usepackage{changepage}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[inline]{enumitem}
\usepackage{enumitem}
\pagestyle{fancy}
\chead{Math 121 - Optimization 1}

\begin{document}
\begin{enumerate}
\item Assume we have a cylindrical can that holds 1 L of liquid. We want to find the minimal amount of metal used to make the can.
\begin{itemize}
\item First, we identify the function we need to optimize. To minimize the amount of metal used, we'll minimize the function that measure the surface area. For a cylinder with radius $r$ and height $h$, the surface area is $$S = 2\pi r^2 + 2 \pi r h$$ 
\item Second, we need a \textit{constraint}. In this case, it's the volume. The volume of a cylinder is $$V = \pi r^2 h,$$ or in this case, $1 = \pi r^2h$, since the volume is 1 liter.
\item Right now the formula for $S$ has 2 variables in it, and we only know how to take the derivative of a function with one variable. You can use the constraint to get rid of one variable. This is done by solving the volume equation for either $r$ or $h$. In this case, it's easier to solve for $h$.
\item Once you have a formula for $h$, replace the $h$ in the formula for $S$. 
\item Now you should have a formula for $S$ that only has one variable, $r$. Take the first derivative, and find the critical points.
\item Find a critical point that is a local minimum. This should be a value for $r$.
\item Use that value of $r$ to find $h$, and then find $S$.
\end{itemize}
\item Suppose we want to enclose a rectangular field. One side of the field has a barn, so we only need 3 sides of the rectangle. If there is only 500 feet of fencing that can be used, find the length and width of the rectangle that contains the largest area.
\begin{itemize}
\item What is the function you are trying to optimize?
\item What is the constraint?
\item Get the function you are trying to optimize down to just one variable, and find the local maximum.
\end{itemize}
\item To inscribe a rectangle in a circle, the rectangle must be inside the circle, with all 4 corners touching the circle. What is the area of the largest rectangle that can be inscribed in a circle of radius 4?
\item Find the point on the curve $y = x^2 + 1$ that is closest to $(0,2)$.
\end{enumerate}

\end{document}