\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{setspace}

\setlength\parindent{0pt}
\usepackage{hyperref}
\usepackage{amssymb,amsthm,amsmath, fancyhdr}
\pagestyle{fancy}

\usepackage{lipsum}

\begin{document}
\chead{Math 121 - Productive Failures for Standards Assessment 1}
Each of these problems is incorrect. Find and fix the mistakes.
\begin{enumerate}
\item
Evaluate the limit, or determine that it does not exist.
$$\lim_{x \rightarrow -2} \frac{x^2 + 5x + 6}{x+2}$$
\\ \textbf{Incorrect Solution}: I plugged in -2, and I got $(-2)^2 + 5(-2) + 6 = 0$ on the top and $(-2) + 2 = 0$ on the bottom. I don't think the limit exists, because you can't divide by zero.
\item
Evaluate the limit, or determine that it does not exist.
$$\lim_{x\rightarrow \infty} \frac{x^2 + x - 1}{x^2 - 1}$$
\\ \textbf{Incorrect Solution}: The top goes to $\infty + \infty - 1$, and the bottom goes to $\infty^2 - 1$. Squaring a number seems bigger than just adding it to itself, so I think the bottom is bigger, and I'll say $$\lim_{x\rightarrow \infty} \frac{x^2 + x - 1}{x^2 - 1} = 0$$
\item 
Evaluate the limit, or determine that it does not exist.
$$\lim_{x \rightarrow 3}  \frac{1}{x^2-9}$$
\\ \textbf{Incorrect Solution}: You can't divide by zero, so the limit doesn't exist.
\item
Use limits to find all vertical and horizontal asymptotes of this function.
$$f(x) = \frac{3x^2 -4}{5x^2 -2}$$
\\ \textbf{Incorrect Solution}: I put this into a graphing calculator and it looks like there is a horizontal asymptote at $y = \frac{1}{2}$ and a vertical asymptote at about $x = \frac{1}{2}$.
\item
Use the definition to show that the given function is continuous at the point $x = 1$.
$$f(x) = \frac{1}{x}$$
\\ \textbf{Incorrect Solution}: I put this into a calculator and I don't see a gap. I also checked and $f(1) = 1$, so I think it's continuous.
\item
Apply the Intermediate Value Theorem to show that the function has a root in the interval [0,4]. State any hypothesis you use.
$$f(x) = x^2 + 2x -4$$
\\ \textbf{Incorrect Solution}: Since $f(0) = -4$ and $f(4) = 20$, the function has to cross the $x-$axis somewhere in there, so there must be a root on that interval.
\item
Find the derivative of the following function, using the limit definition.
$$f(x) = 3x+5$$
\\ \textbf{Incorrect Solution}: I remember a formula that I saw in high school that tells me that the derivative is 3.
\\ \textbf{Incorrect Solution}: I graphed this, and it's a straight line, and the slope of that line is 3, so the derivative is 3.
\\ \textbf{Incorrect Solution}: I remember the formula for the limit definition of the derivative (look it up if you don't remember it), but there is an $h$ in the denominator, and I need the limit as $h$ goes to zero. You can't divide by zero, so the limit doesn't exist, and this function doesn't have a derivative.
\end{enumerate}
\end{document}