\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{fancyhdr}
\usepackage[margin=1.0in]{geometry}
\usepackage{amsmath}
\usepackage{changepage}
\usepackage{graphicx}
\usepackage[inline]{enumitem}
\usepackage{enumitem}
\pagestyle{fancy}
\chead{Math 121 - The Second Derivative Test}

\begin{document}
For each of the functions below, find all of the following:
\begin{itemize}
\item All intervals where the function is concave up.
\item All intervals where the function is concave down.
\item All local extrema, using the second derivative test.
\item All absolute extrema, when they exist.
\end{itemize}
\begin{enumerate}
\item $f(x) = 2x^3 + 5x^2 - \frac{3}{2}x + 1$
\item $g(x) = \sqrt[5]{x}(x+7)$
\item $h(x) = \frac{x^2 -2}{\sqrt{x}}$
\end{enumerate}

For each of these functions, find the value of $x$ that satisfies the Mean Value Theorem on the given interval. Don't forget to check that the hypotheses of the Mean Value Theorem are satisfied. If they're not, you can skip the problems.

\begin{enumerate}
\setcounter{enumi}{3}
\item $g(x) = x^3 - 16x$ on the interval [-4,2].
\item $f(x) = x^2 - 6x + 8$ on the interval [2,5].
\item $h(x) = \frac{x^2 + \sqrt{x}}{x-1}$ on the interval $[0,2]$.
\end{enumerate}
The police can use the Mean Value Theorem to give you a ticket, even when they're not around.
\begin{itemize}
\item Suppose you're driving through a state with EZ-pass toll booths. You pass through one toll booth at mile marker 226 (and it scans your EZ-pass), then through another at mile marker 326 (where the pass is scanned again). The two scans take place 75 minutes apart.
\item Suppose you have a function $p(t)$ that shows the position of the car, with $t$ in hours. Assume $p(0) = 226$. Find the value of $t$, such that $p(t) = 326$.
\item The police claim that this car was traveling 80mph at some point in between these two toll booths. The speed limit is 65mph, so you get a ticket. How was this determined? Try setting it up with the Mean Value Theorem, and remember what you get when you take the derivative of a position function.
\end{itemize}
\end{document}