\documentclass{exam}

\usepackage{amsmath,amssymb,amsthm}

\title{Math 121 - Readiness Assessment \# 3}
\date{}
%Key - D027
\begin{document}
\maketitle

\begin{questions}
\question Which is the correct product rule?
\begin{choices}
\choice $[f(x)g(x)]' = f'(x)g'(x)$
\choice $[f(x)g(x)]' = f'(x)g(x) + g'(x)f(x)$
\choice $[f(x)g(x)]' = f'(x)g(x) - g'(x)f(x)$
\choice $[f(x)g(x)]' = f(x)g(x) + g'(x)f'(x)$
\end{choices}
\question Which is the correct quotient rule?
\begin{choices}
\choice $\left[\frac{f(x)}{g(x)}\right]' = \frac{f'(x)g(x) - g'(x)f(x)}{[g(x)]^2}$
\choice $\left[\frac{f(x)}{g(x)}\right]' = \frac{f(x)g'(x) - g(x)f'(x)}{[g(x)]^2}$
\choice $\left[\frac{f(x)}{g(x)}\right]' = \frac{f'(x)g(x) + g'(x)f(x)}{[g(x)]^2}$
\choice $\left[\frac{f(x)}{g(x)}\right]' = \frac{f'(x)g(x) + g'(x)f(x)}{[f(x)]^2}$
\end{choices}
\question Given $F(x) = f(g(x))$, which is the correct chain rule?
\begin{choices}
\choice $F'(x) = f'(x)g'(x)$
\choice $F'(x) = f'(x)g(x) + g'(x)f(x)$
\choice $F'(x) = f'(g(x))g'(x)$
\choice $F'(x) = f'(g'(x))g(x)$
\end{choices}
\question Which is NOT the equation of a line through the point $(x_1,y_1)$ with slope $m$?
\begin{choices}
\choice $y = mx + b$
\choice $y - y_1 = m(x - x_1)$
\choice $y = m(x - x_1) + y_1$
\choice $y = mx + (y_1-mx_1)$
\end{choices}
\question Given a function $f(x)$, and a point $(x_1,y_1)$ on the graph of $f$, what is the equation of the tangent line touching $f$ at $(x_1,y_1)$?
\begin{choices}
\choice $y - y_1 = f'(x)(x - x_1)$
\choice $y - y_1 = f'(x_1)(x - x_1)$
\choice $y - y_1 = f(x)(x - x_1)$
\choice $y - y_1 = f(x_1)(x - x_1)$
\end{choices}
\question Which of these is an implicit function?\\
\begin{oneparchoices}
\choice $y = 2x^2 + 5x$
\choice $y = \sin(x^2)$
\choice $3x^3 - \tan(x) = y$
\choice $x^2 + y^2 + 2xy$
\end{oneparchoices}
\question Which of these is NOT an implicit function?\\
\begin{oneparchoices}
\choice $y = \sin(xy)$
\choice $x = 3y^2 + y^3 + 7\tan(y)$
\choice $xt = 3x - t^2$
\choice $x = yt + xt - t$
\end{oneparchoices}
\question Which of these is NOT an example of a related rate?
\begin{choices}
\choice As time passes, a population of bacteria grows.
\choice Increasing the rate at which a balloon fills affects the rate at which the surface are of the balloon changes.
\choice Speeding up how fast a ladder slides down a wall changes how fast the other end of the ladder moves away from the wall.
\choice The speed of sand up a conveyor belt affects the volume of the sandpile below.
\end{choices}
\question Which differentiation rule is specifically recommended in the strategy for solving related rates problems?
\begin{choices}
\choice Product Rule
\choice Quotient Rule
\choice Chain Rule
\choice Power Rule
\end{choices}
\question In the following problem, identify the rates that would be related when setting up the problem.
\begin{center}
Car $A$ is traveling west at 50kph and car $B$ is traveling north at 60kph. Both are headed for the intersection of 2 roads. How fast are the cars approaching each other when $A$ is 0.3km and $B$ is 0.4km from the intersection?
\end{center}
\begin{choices}
\choice The speeds of the cars and their distances from the intersection.
\choice The distances of each car from the intersection after 1 hour.
\choice The change in the speed of each car.
\choice The speeds of the cars and the change in the distance between them.
\end{choices}
\end{questions}
\end{document}