\documentclass{exam}

\usepackage{amsmath,amssymb,amsthm}

\title{Math 121 - Readiness Assessment \# 2}
\date{September 24, 2018}
%Key - D026
\begin{document}
\maketitle

\begin{questions}
\question The tangent line to $y = f(x)$ at the point $(a, f(a))$ has slope equal to...
\begin{choices}
\choice $\lim_{x\rightarrow a} f(x)$
\choice $f(a)$
\choice $f(a+h)$
\choice $f'(a)$
\end{choices}
\question Which of these is a case where the derivative can exist?
\begin{choices}
\choice A horizontal tangent
\choice A sharp corner
\choice A discontinuity
\choice A vertical tangent
\end{choices}
\question If a function $f(x)$ is differentiable at a point $a$, what must also be true?
\begin{choices}
\choice $f(x)$ is a polynomial.
\choice $f(x)$ is continuous at $a$.
\choice $f(x)$ has an infinite limit.
\choice $f(x)$ does not exist at $a$.
\end{choices}
\question The derivative of the function $f(x) = x^n$ is
\begin{choices}
\choice $x$
\choice $(n-1)x^{n+1}$
\choice $nx^{n-1}$
\choice $n$
\end{choices}
\question What does the notation $(f \circ g)(x)$ or $f(g(x)$ mean?
\begin{choices}
\choice Take a value for $x$, apply the function $f$, then apply the function $g$.
\choice Multiply the value of $x$ by $g$, then multiply it by $f$.
\choice Take a value for $x$, apply the function $g$, then apply the function $f$.
\choice Multiply the value of $x$ by $f$, then multiply it by $g$.
\end{choices}
\question Which of the following is not a rule from the most recent reading? 
\begin{choices}
\choice Exponent Rule
\choice Product Rule
\choice Quotient Rule
\choice Chain Rule
\end{choices}
\question We saw in the reading that $\frac{d}{dx} \sin(x) = \cos(x)$ and that $\frac{d}{x} \cos(x) = -\sin(x)$. Which rule was used to show that $\frac{d}{dx} \tan(x) = \sec^2(x)$?
\begin{choices}
\choice Product Rule
\choice Chain Rule
\choice Quotient Rule
\choice O'doyle Rules!
\end{choices}
\question The Chain Rule is necessary when we have to find the derivative of a
\begin{choices}
\choice Product of functions
\choice Compositions of functions
\choice Quotient of functions
\choice Discontinuous functions
\end{choices}
\question Our text shows use multiple ways of writing the derivative. Pick the one that does not appear.
\begin{choices}
\choice $f'(x)$
\choice $\frac{df}{dx}$
\choice $D_xf(x)$
\choice Diff $(x)$
\end{choices}
\question Which is not a differentiation formula from the reading?
\begin{choices}
\choice $\frac{d}{dx}[f(x)g(x)] = f(x) \frac{d}{dx}[g(x)] + g(x)\frac{d}{dx}[f(x)]$
\choice If $F(x) = f(g(x))$, then $F'(x) = f'(x)\cdot g'(x)$
\choice $\frac{d}{dx}\left[\frac{f(x)}{g(x)}\right] = \dfrac{g(x)\frac{d}{dx}[f(x)] - f(x)\frac{d}{dx}[g(x)]}{[g(x)]^2}$
\choice If $F(x) = f(g(x))$, then $F'(x) = f'(g(x))\cdot g'(x)$
\end{choices}
\end{questions}
\end{document}