\documentclass{exam}

\usepackage{amsmath,amssymb,amsthm}

\title{Math 121 - Standards Assessment \# 3}
\date{October 19, 2018}

\begin{document}
\maketitle
\bigskip

  \fbox{\parbox{6in}{
    \vspace{10pt}
    \textbf{\large Your Name:}
    \vspace{10pt}
  }}
\begin{center}
\large
    For any problem you skip, place a line through the problem number and the objective number next to it. For any problem you want graded, circle the problem number and the objective number next to it.
\end{center}
\normalsize

\begin{enumerate}
\item Possible Objectives: 1\\
Evaluate the limit, or determine that it does not exist.
$$\lim_{x \rightarrow -2} \frac{x^2 + 6x + 8}{x+2}$$
\item Possible Objectives: 2\\
Evaluate the limit, or determine that it does not exist.
$$\lim_{x\rightarrow \infty} \frac{x^3 + 5x - 1}{5x^2 +4}$$
\item Possible Objectives:1, 3\\
Evaluate the limit, or determine that it does not exist.
$$\lim_{x \rightarrow 3}  \frac{2x}{3-x}$$
\item Possible Objectives: 1,2,3,4\\
Use limits to find all vertical and horizontal asymptotes of this function.
$$f(x) = \frac{3x^2 -4}{2x^2 - 2}$$
\item Possible Objectives:1, 5\\
Use the definition to show that the given function is \textbf{not} continuous at the point $x = 1$.
$$f(x) = \left\{ \begin{array}{rl} 2x+1 & \mbox{if } x \neq 5 \\ 3 & \mbox{if } x = 5\end{array}\right.$$
\item Possible Objectives:6\\
Apply the Intermediate Value Theorem to show that the function has a root in the interval [0, $\pi$]. State any hypothesis you use.
$$f(x) = \cos(x)$$
\item Possible Objectives:1, 7\\
Find the derivative of the following function, using the limit definition.
$$f(x) = 5 - 2x$$
\item Possible Objectives: 8\\
Find the derivative of $$y = \frac{4x^2 + \sqrt{x}}{x}$$ without using the quotient rule.
\item Possible Objectives: 9\\
Given $y = \sec{\theta}$, find $\frac{dy}{d\theta}$
\item Possible Objectives: 8, 9, 10\\
Find the first derivative of $$f(x) = \tan(x)(3x^5 - \sqrt{x})$$
\item Possible Objectives: 8, 9, 11\\
Find the first derivative of $$f(x) = \frac{\tan(x)}{3x^5 - \sqrt{x}}$$
\item Possible Objectives: 8, 9, 12\\ 
Find the first derivative of $$f(x) = \tan{3x^5 - \sqrt{x}}$$
\item Possible Objectives: 8, 9, 10, 11, 12, 13\\
Find the first derivative of $$f(x) = \frac{\tan(3x^3)(2- \sqrt{x})}{\cos(x + 5)}$$
\item Possible Objectives: 8, 9, 10, 11, 12, 13, 14\\
Find the equation of the tangent line to the curve $y = x^3 + \cos(x)$ at the point $x = 0$.
\item Possible Objectives: 8, 9, 10, 11, 12, 13, 15\\
Find $\frac{dy}{dt}$
$$xy = 2y^3$$
\item Possible Objectives: 8, 9, 10, 11, 12, 13, 15, 16, 17\\
A 15 foot ladder is resting against the wall. The bottom is initially 10 feet away from the wall and is being pushed towards the wall at a rate of 1/4 ft/sec. How fast is the top of the ladder moving up the wall 12 seconds after we start pushing? (Note that this can count for objectives 16 and 17. Be very clear with your setup.)
\end{enumerate}
\end{document}