\documentclass{exam}

\usepackage{amsmath,amssymb,amsthm}

\title{Math 121 - Standards Assessment \# 2}
\date{October 5, 2017}

\begin{document}
\maketitle
\bigskip

  \fbox{\parbox{6in}{
    \vspace{10pt}
    \textbf{\large Your Name:}
    \vspace{10pt}
  }}
\begin{center}
\large
    For any problem you skip, place a line through the problem number and the objective number next to it. For any problem you want graded, circle the problem number and the objective number next to it.
\end{center}
\normalsize

\maketitle

\begin{enumerate}
\item Possible Objectives: 1\\
Evaluate the limit, or determine that it does not exist.
$$\lim_{x \rightarrow 3} \frac{x^2 - 5x+6}{x-3}$$
\item Possible Objectives: 2\\
Evaluate the limit, or determine that it does not exist.
$$\lim_{x\rightarrow \infty} \frac{1-2x + 4x^4}{2 + x^5}$$
\item Possible Objectives:1, 3\\
Evaluate the limit, or determine that it does not exist.
$$\lim_{x \rightarrow 3+}  \frac{x+2}{x-3}$$
\item Possible Objectives: 1,2,3,4\\
Use limits to find all vertical and horizontal asymptotes of this function.
$$f(x) = \frac{2x^2 +x-1}{x^2 +x-2}$$
\item Possible Objectives:1, 5\\
Use the definition to show that the given function is continuous at the point $x = 3$.
$$f(x) = 2x^2 + 5$$
\item Possible Objectives:6\\
Apply the Intermediate Value Theorem to show that the function has a root in the interval [-2,1]. State any hypothesis you use.
$$f(x) = x + 1$$
\item Possible Objectives:1, 7\\
Find the derivative of the following function, using the limit definition.
$$f(x) = x^2 - 4$$
\item Possible Objectives: 8\\
Find $\frac{dy}{dx}$. $$y = x^4 - 2x^3 + 1$$
\item Possible Objectives: 9\\
Find $g'(x)$. $$g(x) = \cos(x)$$
\item Possible Objectives: 8, 9, 10\\
Differentiate the given function.
$$f(x) = 2x^5\sin(x)$$
\item Possible Objectives: 8, 9, 11\\
Differentiate the given function.
$$f(x) = \frac{2x^5}{\sin(x)}$$
\item Possible Objectives: 8, 9, 12\\ 
Differentiate the given function.
$$y = \sin(2x^5)$$
\item Possible Objectives: 8, 9, 10, 11, 12, 13\\
Differentiate the given function.
$$g(x) = \frac{\cos(x)\sqrt{2x^2 +x}}{x + \tan(x)}$$
\item Possible Objectives: 8, 9, 10, 11, 12, 13, 14\\
Find the equation of the tangent line to the curve $y = x^3$ at the point $x = -1$.
\end{enumerate}
\end{document}