\documentclass{exam}

\usepackage{amsmath,amssymb,amsthm,graphicx}

\title{Math 121 - Standards Assessment \# 6}
\date{December 11, 2019}

\begin{document}
\maketitle
\bigskip

  \fbox{\parbox{6in}{
    \vspace{10pt}
    \textbf{\large Your Name:}
    \vspace{10pt}
  }}
\begin{center}
\large
    For any problem you skip, place a line through the problem number and the objective number next to it. For any problem you want graded, circle the problem number and the objective number next to it.
\end{center}
\normalsize

\begin{enumerate}
\item Possible Objectives: 1\\
Evaluate the limit, or determine that it does not exist.
$$\lim_{x \rightarrow 0} \frac{|x|}{x}$$
\item Possible Objectives: 2\\
Evaluate the limit, or determine that it does not exist.
$$\lim_{x\rightarrow \infty} \frac{6x^4 + 5}{3x^4 - 5x + 6}$$
\item Possible Objectives:1, 3\\
Evaluate the limit, or determine that it does not exist.
$$\lim_{x \rightarrow 0+} \frac{1}{x}$$
\item Possible Objectives: 1,2,3,4\\
Use limits to find all vertical and horizontal asymptotes of this function.
$$g(x) = \frac{x-3}{2x^2 -1}$$
\item Possible Objectives:1, 5\\
Use the definition to show that the given function is not continuous at the point $x = 0$.
$$f{x} = \frac{5}{x^2 - 2x}$$
\item Possible Objectives:6\\
Apply the Intermediate Value Theorem to show that the function has a root in the interval [-7,7]. State any hypothesis you use.
$$g(x) = x-2$$
\item Possible Objectives:1, 7\\
Find the derivative of the following function, using the limit definition.
$$g(x) = 5 + 2x^2$$
\item Possible Objectives: 8\\
Differentiate using the power rule. 
$$f(x) = \frac{x^2 -1}{\sqrt{x}}$$
\item Possible Objectives: 9\\
Given $$f(x) = \sin(x) - \cos(x)$$, find $f'(x)$
\item Possible Objectives: 8, 9, 10\\
Find the first derivative of $g(x) = \sin(x)\cos(x)$

\item Possible Objectives: 8, 9, 11\\
Find the first derivative of $f(x) = \frac{5x^2}{\cos(x)}$

\item Possible Objectives: 8, 9, 12\\ 
Find the first derivative of $f(x) = \cos^2(x) - 5\cos(x) + 6$
\item Possible Objectives: 8, 9, 10, 11, 12, 13\\
Find the first derivative of $g(x) = \frac{(4x^5\cos(x))^5}{\sin(x)}$

\item Possible Objectives: 8, 9, 10, 11, 12, 13, 14\\
Find the equation of the tangent line to the curve $y = \sin(x) + 2x$ at the point $(0,0)$.
\item Possible Objectives: 8, 9, 10, 11, 12, 13, 15\\
Find $\frac{dy}{dx}$
$$1 + xy = y^2 - x$$
\item Possible Objectives: 8, 9, 10, 11, 12, 13, 15, 16, 17\\
Two cars start at the same spot. One drives due north at 55mph, and the other drives due west at 45mph. How fast is the difference between the two cars changing one hour after they start driving? (Note that this can count for objectives 16 and 17. Be very clear with your setup.)
\item Possible Objectives: 8, 9, 10, 11, 12, 13, 18
Find all intervals on which the function $f(x) = x^3 - 7x -6$
 is increasing and decreasing.
\item Possible Objectives: 8, 9, 10, 11, 12, 13, 19
Find all intervals on which the function $f(x) = x^3 - 7x -6$
 is concave up and concave down.
\item Possible Objectives: 8, 9, 10, 11, 12, 13, 20
Find all critical values of the function $f(x) = x^3 - 7x -6$
\item Possible Objectives: 8, 9, 10, 11, 12, 13, 20, 21
Find all local maxima and minima of this function, using the first derivative test.
$f(x) = x^3 - 7x -6$
\item Possible Objectives: 8, 9, 10, 11, 12, 13, 20, 22
Find all local maxima and minima of this function, using the second derivative test.
$f(x) = x^3 - 7x -6$
\item Possible Objectives: 8, 9, 10, 11, 12, 13, 20, 21, 22, 23
Find the absolute maximum and minimum values of $f(x) = x^3 - 7x -6$ on the interval [-5,5].
\item Possible Objectives: 8, 9, 10, 11, 12, 13, 24
Find the value which satisfies the Mean Value Theorem for the function $f(x) = x^3 - 7x -6$ on the interval $[4,6]$.
\item Possible Objectives: 8, 9, 10, 11, 12, 13, 20, 21, 22, 25, 26
If a cylinder needs to hold exactly 1500ml of liquid, what are the height and radius of the can that will minimize the surface area of metal used? (Note that this can count for objectives 25 and 26. Be very clear with your setup.)
\item Possible Objectives: 27\\
Find an antiderivative of the given polynomial.
$f(x) = \frac{2x^5 + 3x^4}{x^2}$
\item Possible Objectives: 28\\
Find the antiderivative of the given trig function.
$f(x) = \cos(x) - \sec^2(x)$.
\item Possible Objectives: 29\\
Use a finite summation with $n=4$ to approximate the area under the function $y = x^3$ over the interval $[1,2]$. Use left endpoints.
\item Possible Objectives: 30\\
Express the definite integral for the function $y = x^3$ over the interval $[1,2]$ using a Riemann Sum.
\item Possible Objectives: 31\\
Evaluate the given defininte integral.
$$\int_{-1}^1 x^3 + 4x^2 - 6x + 1 dx$$
\item Possible Objectives: 27, 28, 32\\
Evaluate the given indefinite integral.
$$\int \sin(x) + 3x^7 dx$$
\item Possible Objectives: 27, 28, 32, 33\\
Evalute the given indefinite integral.
$$\int 12x^3\sin(3x^4) dx$$
\item Possible Objectives: 34\\
Find the derivative of the given function.
$$f(x) = 5\ln(x) + 1$$
\item Possible Objectives: 35\\
Find the derivative of the given function.
$$f(x) = e^{4x^2 + 6x - 9}$$
\item Possible Objectives: 15, 34, 36\\
Find the derivative of the given function.
$$y =x^{\sin(x)}$$
\item Possible Objectives: 37\\
Find the derivative of the given function.
$$f(x) = \tan^{-1}(x^2)$$
\item Possible Objectives: 38\\
Evaluate the limit or show that it does not exist. Verify first that you have an indeterminate form. $$\lim_{x\rightarrow 0} \frac{x}{\sin(x)}$$
\end{enumerate}
\end{document}