\documentclass{exam}

\usepackage{amsmath,amssymb,amsthm,graphicx}

\title{Math 121 - Standards Assessment \# 4}
\date{November 6, 2018}

\begin{document}
\maketitle
\bigskip

  \fbox{\parbox{6in}{
    \vspace{10pt}
    \textbf{\large Your Name:}
    \vspace{10pt}
  }}
\begin{center}
\large
    For any problem you skip, place a line through the problem number and the objective number next to it. For any problem you want graded, circle the problem number and the objective number next to it.
\end{center}
\normalsize

\begin{enumerate}
\item Possible Objectives: 1\\
Evaluate the limit, or determine that it does not exist.
$$\lim_{x \rightarrow -2} \left\{\begin{array}{rl} 2x-1 & \mbox{if } x \leq -2 \\ x & \mbox{if } x > -2 \end{array}\right.$$
\item Possible Objectives: 2\\
Evaluate the limit, or determine that it does not exist.
$$\lim_{x\rightarrow \infty} \frac{x^4 + 5x - 1}{5x^5 +4x^2 - 2}$$
\item Possible Objectives:1, 3\\
Evaluate the limit, or determine that it does not exist.
$$\lim_{x \rightarrow 5}  \frac{2x^2 + 1}{x^2 - 25}$$
\item Possible Objectives: 1,2,3,4\\
Use limits to find all vertical and horizontal asymptotes of this function.
$$f(x) = \frac{x^2 + 5x + 6}{x^2 + 7x + 10}$$
\item Possible Objectives:1, 5\\
Use the definition to show that the given function is continuous at the point $x = 0$.
$$f(x) = \left\{ \begin{array}{rl} 2x+1 & \mbox{if } x \leq 0 \\ 3x+1 & \mbox{if } x > 0\end{array}\right.$$
\item Possible Objectives:6\\
Apply the Intermediate Value Theorem to show that the function has a root in the interval [-2,2]. State any hypothesis you use.
$$f(x) = \tan(x)$$
\item Possible Objectives:1, 7\\
Find the derivative of the following function, using the limit definition.
$$f(x) = x^2 + x + 1$$
\item Possible Objectives: 8\\
Find the derivative of $$y = 5\sqrt{x} + 3x^5$$ 
\item Possible Objectives: 9\\
Given $y = \sin{\theta}$, find $\frac{dy}{d\theta}$
\item Possible Objectives: 8, 9, 10\\
Find the first derivative of $$f(x) = \sin(x)(3x^3 - \tan(x))$$
\item Possible Objectives: 8, 9, 11\\
Find the first derivative of $$f(x) = \frac{\sin(x)}{3x^5 - \tan(x)}$$
\item Possible Objectives: 8, 9, 12\\ 
Find the first derivative of $$f(x) = \sin{3x^5 - \tan(x)}$$
\item Possible Objectives: 8, 9, 10, 11, 12, 13\\
Find the first derivative of $$f(x) = \cos\left(\frac{2x^2\sin(x)}{x^2 +5}\right)$$
\item Possible Objectives: 8, 9, 10, 11, 12, 13, 14\\
Find the equation of the tangent line to the curve $y = \sin^2(x)$ at the point $x = \pi/4$.
\item Possible Objectives: 8, 9, 10, 11, 12, 13, 15\\
Find $\frac{dy}{dt}$
$$\sqrt{xy} = 2y^2 + 2x^2$$
\item Possible Objectives: 8, 9, 10, 11, 12, 13, 15, 16, 17\\
A 2m man is walking towards a 6m lightpost at 2m/s. How fast is the tip of his shadow moving towards the post when he is 10m away from the lightpost? (Note that this can count for objectives 16 and 17. Be very clear with your setup.)
\item Possible Objectives: 8, 9, 10, 11, 12, 13, 18
Find all intervals on which the function $f(x) = \frac{1}{3}x^3 + \frac{7}{2}x^2 + 10x + 1$ is increasing and decreasing.
\item Possible Objectives: 8, 9, 10, 11, 12, 13, 19
Find all intervals on which the function $f(x) = \frac{1}{3}x^3 + \frac{7}{2}x^2 + 10x + 1$ is concave up and concave down.
\item Possible Objectives: 8, 9, 10, 11, 12, 13, 20
Find all critical values of the function $g(x) = x^3 - 9x^2 + 15x - 7$.
\item Possible Objectives: 8, 9, 10, 11, 12, 13, 20, 21
Find all local maxima and minima of this function, using the first derivative test.
$$f(x) = x^3 - 9x^2 + 15x - 7$$
\item Possible Objectives: 8, 9, 10, 11, 12, 13, 20, 22
Find all local maxima and minima of this function, using the second derivative test.
$$f(x) = x^3 - 9x^2 + 15x - 7$$
\item Possible Objectives: 8, 9, 10, 11, 12, 13, 20, 21, 22, 23
Find the absolute maximum and minimum values of $y = x^{2/3}$ on the interval [-2,3].
\item Possible Objectives: 8, 9, 10, 11, 12, 13, 24
Find the value which satisfies the Mean Value Theorem for the function $f(x) = 2x^2 + 3x - 1$ on the interval $[4,6]$.
\item Possible Objectives: 8, 9, 10, 11, 12, 13, 20, 21, 22, 25, 26
A farmer has 2400 ft of fencing and wants to fence off a rectangular field that borders a straight river. He needs no fence along the river. What are the dimensions of the field that has the largest area? (Note that this can count for objectives 25 and 26. Be very clear with your setup.)
\end{enumerate}
\end{document}