\documentclass{exam}

\usepackage{amsmath,amssymb,amsthm}

\title{Math 121 - Standards Assessment \# 1}
\date{September 20, 2018}

\begin{document}
\maketitle
\bigskip

  \fbox{\parbox{6in}{
    \vspace{10pt}
    \textbf{\large Your Name:}
    \vspace{10pt}
  }}
\begin{center}
\large
    For any problem you skip, place a line through the problem number and the objective number next to it. For any problem you want graded, circle the problem number and the objective number next to it.
\end{center}
\normalsize

\maketitle

\begin{enumerate}
\item Possible Objectives: 1\\
Evaluate the limit, or determine that it does not exist.
$$\lim_{x \rightarrow 1} \frac{x^2 - 2x+1}{x-1}$$
\item Possible Objectives: 2\\
Evaluate the limit, or determine that it does not exist.
$$\lim_{x\rightarrow \infty} \frac{7x^2 + 5x - 1/3}{5x^3 +43}$$
\item Possible Objectives:1, 3\\
Evaluate the limit, or determine that it does not exist.
$$\lim_{x \rightarrow 1}  \frac{x}{2x-2}$$
\item Possible Objectives: 1,2,3,4\\
Use limits to find all vertical and horizontal asymptotes of this function.
$$f(x) = \frac{2x^2 -4}{x^2 + 1}$$
\item Possible Objectives:1, 5\\
Use the definition to show that the given function is continuous at the point $x = 1$.
$$f(x) = \frac{1}{x}$$
\item Possible Objectives:6\\
Apply the Intermediate Value Theorem to show that the function has a root in the interval [0,3]. State any hypothesis you use.
$$f(x) = 2x - x^2 + 1$$
\item Possible Objectives:1, 7\\
Find the derivative of the following function, using the limit definition.
$$f(x) = 3x+5$$
\item Possible Objectives: 8, 9, 10, 11, 12, 13\\
\item Possible Objectives: 8, 9, 10, 11, 12, 13, 14\\
\end{enumerate}
\end{document}